The Talking Heads Experiment

### 2015-04-17 chap4/chap4.tex
orphans, widows, line breaks

This chapter addressed the problem of how agents may 
categorise their environment using information 
on sensory channels about each segment in the scene. 
I argued in favor of a selectionist approach, which 
generates possible solutions in a relatively 
random growth process and tests them in the 
cases presented by the environment. 
This approach contrasts with instructionism, where
the agent is assumed to make gradual abstraction 
from a series of examples using induction, and with 
a rationalist approach, where perceptually grounded categories are
assumed to be innate and hence derived through 
genetic evolution.

>>>>

This chapter addressed the problem of how agents may 
categorise their environment using information 
on sensory channels about each segment in the scene. 
I argued in favour of a selectionist approach, which 
generates possible solutions in a relatively 
random growth process and tests them in the 
cases presented by the environment. 
This approach contrasts with instructionism, where
the agent is assumed to make gradual abstraction 
from a series of examples using induction, and with 
a rationalist approach, where perceptually grounded categories are
assumed to be innate and hence derived through 
genetic evolution.
